% !TEX root = ../../root.tex
\subsection{decaWave DWM1000 module}

The DWM1000 is an UWB wireless transceiver module designed for easy adoption in two-way ranging schemes.
It is based around the DW1000, an integrated low-power, single chip CMOS RF transceiver IC compliant with the \emph{IEEE802.15.4-2011 UWB} standard, and has been chosen because it required no RF design: the antenna and associated RF circuitry are already on the module.

Along with typical RF modules capabilities such as configurable power modes and data transmission rates, the module can use custom, proprietary leading-edge detection algorithm which --- along with configurable preamble size and optional, non-standard frame delimiter --- can provide accurate timestamping of incoming and departing messages.

The module contains an \SI{38.4}{\mega\hertz} reference crystal used by the SPI interface and the transmitter for signal modulation and timestamps generation.
Its accuracy is ensured by a factory trimming process which brings the frequency offset down to about \SI{2}{ppm}.
The on-chip crystal trimming circuit and temperature sensor allows for dynamic temperature compensation.

Interfacing with the device is achieved through an SPI bus that can run at up to \SI{20}{\mega\hertz}.
Other data connections include the interrupt (IRQ) and reset (RST) signal.
The bus configuration (sampling polarity and phase) can be customized by manipulating the GPIO pins, which are also routed to the microcontroller.


In laying out the board for PCB manufacturing, attention has been paid towards the guidelines included in the datasheet, which suggests a keep-out area of \SI{1}{\centi\meter} around the antenna section of the module, plus a board-wide ground plane.
